%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Troubleshooting.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Troubleshooting}

In this section, possible errors are listed along with their troubleshooting solutions.

\section{Hardware Troubleshooting}

\begin{enumerate}
	\item The system does not power ON. 
	\begin{itemize}
		\item Check the connectivity with USB-C cable and verify the power source. Ensure the USB cable is functioning properly.
	\end{itemize}
	\item The system camera is not functioning, unable to capture images.
	\begin{itemize}
		\item Verify that the Vision Shield is properly mounted to the Portenta H7 system. Test the camera with a simple sketch in the Arduino IDE.
	\end{itemize}
\end{enumerate}

\section{Software Troubleshooting}
\begin{enumerate}
	\item The model fails to deploy using the Arduino CLI. 
	\begin{itemize}
		\item Ensure the correct board core is installed. Recheck the compile and upload commands.
	\end{itemize}
	\item The system outputs recognition results with low accuracy rate.
	\begin{itemize}
		\item Improve lighting conditions and ensure faces are properly aligned with the camera. Re-train the model with more diverse datasets.
	\end{itemize}
	\item The Edge Impulse CLI cannot detect the Portenta H7.
	\begin{itemize}
		\item Restart the device and reconnect it to your computer. Ensure the correct port is selected in the Arduino CLI.
		\item Verify that the Edge Impulse CLI is correctly installed.
	\end{itemize}
\end{enumerate}




